---
title: "Titanic Notebook"
author: "Tharso Rossiter"
date: "2/15/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(plyr)
library(dbplyr)
library(readr)
library(partykit)
library(naniar)
```

## Data and objective

Survival	:Survival	0 = No, 1 = Yes
pclass :	Ticket class	1 = 1st, 2 = 2nd, 3 = 3rd
sex	: Sex	
Age	: Age in years	
sibsp	: # of siblings / spouses aboard the Titanic	
parch	: # of parents / children aboard the Titanic	
ticket :	Ticket number	
fare :	Passenger fare	
cabin :	Cabin number	
embarked :	Port of Embarkation	C = Cherbourg, Q = Queenstown, S = Southampton
  

Objecive : predict Survival based on the other variables.

## Importing data

```{r importing data}
test <- read_csv('test.csv', col_names = TRUE)
train <- read_csv('train.csv', col_names = TRUE)
```

We will create an "All" dataset joining both training and test data.

```{r joining datasets}
test$Survived <- NA
All <- rbind(train,test)
```

## Adjusting Data Types

We will check the data types and adjust those according to our necessity.

```{r viweing data types}
str(All)
```

* Survived should be a factor
* Pclass should be a factor
* Sex should be a factor
* Cabin should be a factor
* Embraked should be a factor

```{r factorising variables}
All$Survived <- as.factor(All$Survived)
All$Pclass <- as.factor(All$Pclass)
All$Sex <- as.factor(All$Sex)
All$Cabin <- as.factor(All$Cabin)
All$Embarked <- as.factor(All$Embarked)
```



## Dealing with missing values

Using naniar package to visualise missing data in our train set:

```{r visualising missing data}
vis_miss(All[!is.na(All$Survived),])
```

Age and Cabin are missing values.

We will use a conditional partitioning tree to fit Age variables.

```{r ctree age}
agefit <- ctree(Age ~ Sex + SibSp + Pclass + Parch + Fare + Embarked,
                data = All[!is.na(All$Age),])
All$Age[is.na(All$Age)] <- predict(agefit, All[is.na(All$Age),])
```


## Logistic Regression

Using logistic regression to estimate survival.

```{r logistic regression}
logfit <- glm(Survived~ Pclass + Sex + Age + SibSp + Parch + Fare + Embarked,
              family = 'binomial',
              data = All[!is.na(All$Survived),])
```

## Fitting Values and Creating CSV file

```{r fit and create csv}
fitted <- predict(logfit,All[is.na(All$Survived),], type = 'response')
fitted <- ifelse(fitted < .66, 0, 1)

df <- data.frame(PassengerId = All[is.na(All$Survived),]$PassengerId, Survived = fitted)
write.csv(df, file = 'log_regression_submit_.66', row.names = FALSE)
```

## Cross-Validation

```{r teste p 1}
train <- All[!is.na(All$Survived),]
test <- All[is.na(All$Survived),]

trainsample <- sample(1:nrow(train), size = floor(nrow(train)/10), replace = TRUE)
train.cvset <- train[trainsample,]
train.trainset <- train[-trainsample,]

pvector <- seq(0.1,0.9,0.1)
error.vector <- rep(NA,9)

for(i in 1:length(pvector)){
  fit <- glm(Survived~ Pclass + Sex + Age + SibSp + Parch + Fare + Embarked,
              family = 'binomial',
              data = train.trainset)
  sur.fitted <- predict(logfit,train.cvset, type = 'response')
  sur.fitted <- ifelse(sur.fitted < pvector[i], 0, 1)
  
  error.vector[i] <- sum(sur.fitted != train.cvset$Survived)
}

plot(error.vector, type = 'l')
```

```{r teste p 2}
pvector2 <- seq(0.6,0.8,0.01)
error.vector2 <- rep(NA,9)

for(i in 1:length(pvector)){
  fit <- glm(Survived~ Pclass + Sex + Age + SibSp + Parch + Fare + Embarked,
              family = 'binomial',
              data = train.trainset)
  sur.fitted <- predict(logfit,train.cvset, type = 'response')
  sur.fitted <- ifelse(sur.fitted < pvector[i], 0, 1)
  
  error.vector2[i] <- sum(sur.fitted != train.cvset$Survived)
}

plot(error.vector2, type = 'l')
```

